---
title: "Appendix S1"
author: "Marc Weber"
date: "1/6/2022"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Background
This code uses network navigation to select upstream and downstream segments within a 5 km range of each site and generates distances for each stressor within 5km of each site as follows:
1.	Downstream crossings: a record (row) for every downstream crossing with columns of BCG site and values would be distance downstream
2.	Upstream crossings: same as 1, but upstream crossings with distance upstream
3.	Small Lakes Upstream: record (row) for every small upstream lake with columns for each BCG site and then value of distance upstream
4.	Large Downstream Lakes: record (row) of every large downstream lake with columns for each BCG site and value of distance downstream

### Setup
```{r, warning=FALSE, message=FALSE}
library(readr)
library(nhdplusTools)
library(sf)
library(dplyr)
library(tigris)
library(mapview)
library(leaflet)
library(ggplot2)
library(rmapshaper)
library(reticulate)
sessionInfo()
```

### Load data
The data used is from [King County Freshwater Benthic Macroinvertebrate Sampling and Analysis Plan](https://pugetsoundstreambenthos.org/). The data citation is:
King County. 2020. King County Freshwater Benthic Macroinvertebrate Sampling and Analysis Plan. Prepared by Kate Macneale, Liora Llewellyn, and Beth Sosik. Water and Land Resources Division. Seattle, Washington. https://pugetsoundstreambenthos.org/
```{r, error=FALSE, message=FALSE, comment=FALSE , eval=FALSE}
sites <- read_csv('Multiscale Framework King County and Puget Lowland data.csv')
sites <- sites %>% 
  dplyr::select(SITE_ID = Location_ID, Latitude, Longitude, COMID)
sites <- sites %>%
  st_as_sf(coords = c("Longitude", "Latitude"), crs = 4269, remove = FALSE)
```

### Create Road-Stream Crossings 
Download US Census Bureau Tiger Line files representing roads and calculate crossings with NHDPlusHR stream lines
```{r, error=FALSE, message=FALSE, comment=FALSE , eval=FALSE}
Sys.getenv('TIGRIS_CACHE_DIR')
options(tigris_use_cache=TRUE)
options(tigris_refresh=TRUE)
counties <- tigris::counties(state='Washington')
sites <- st_join(sites, counties[,c('NAME')])
county_list <- levels(as.factor(sites$NAME))
for (i in 1:length(county_list)){
  if (i==1) roads <- tigris::roads("WA",county_list[i]) else{
    temp <- roads <- tigris::roads("WA",county_list[i])
    roads <- rbind(roads, temp)
  }
}

flowlines_1708 <- read_sf(dsn='NHDPLUS_H_1708_HU4_GDB.gdb',layer='NHDFlowline')
flowlines_1710 <- read_sf(dsn='NHDPLUS_H_1710_HU4_GDB.gdb',layer='NHDFlowline')
flowlines_1711 <- read_sf(dsn='NHDPLUS_H_1711_HU4_GDB.gdb',layer='NHDFlowline')

flowlines <- rbind(flowlines_1708, flowlines_1710, flowlines_1711)

flowlines <- st_zm(flowlines, drop=TRUE, what="ZM")
road_strms <- st_intersection(flowlines, roads)
rm(flowlines_1708, flowlines_1710, flowlines_1711)
flowlines <- st_transform(flowlines, st_crs(sites))
indexes <- get_flowline_index(flowlines,                             sf::st_geometry(sites),
                              search_radius = 300,
                              max_matches = 1)
sites$id <- 1:nrow(sites)
sites <- left_join(sites,indexes, by = "id")
```

## NABD dams
Apply weights to dams and reference to NHDPlusHR in Puget Sound
```{r, error=FALSE, message=FALSE, comment=FALSE, eval=FALSE}
dams <- read_sf('NABD.shp')
sites <- st_transform(sites, st_crs(dams))
dams <- dams %>% 
  dplyr::filter(State=='WA')
dams <- st_crop(dams, st_bbox(sites))
# generate weights, drop unneeded fields
dams <- dams %>% 
  mutate(NID_height=NID_height*0.30488) %>%
  mutate(down_weight = case_when(
    NID_height >= 15 ~ 0,
    NID_height < 15 ~ .5,
     TRUE ~ 1)) %>%
  mutate(up_weight = case_when(
    NID_height >= 15 ~ .25,
    NID_height < 15 ~ .8,
     TRUE ~ 1)) %>%
  dplyr::select(NIDID,Longitude,Latitude,Dam_name,Dam_type,NID_height,Dam_length,NrmStorM3,NIDStorM3,down_weight, up_weight)

flowlines <- st_transform(flowlines, st_crs(dams))
```

### Linear referencing
Use linear referencing to reference sites and dams to NHDPlusHR flowlines in Puget Sound
```{python, eval=FALSE}
import arcpy
# Execute LocateFeaturesAlongRoutes
pts = 'Puget_NABD.shp'
nhd1 = 'L:/Priv/CORFiles/Geospatial_Library_Projects/IWI/BCGs/Puget 2020/Marc/NHDPLUS_H_1708_HU4_GDB.gdb/NHDFlowline'
nhd2 = 'L:/Priv/CORFiles/Geospatial_Library_Projects/IWI/BCGs/Puget 2020/Marc/NHDPLUS_H_1710_HU4_GDB.gdb/NHDFlowline'
nhd3 = 'L:/Priv/CORFiles/Geospatial_Library_Projects/IWI/BCGs/Puget 2020/Marc/NHDPLUS_H_1711_HU4_GDB.gdb/NHDFlowline'

props = "RID POINT MEAS"
arcpy.LocateFeaturesAlongRoutes_lr(pts, nhd1, "REACHCODE", "1000 Meters", "Puget_NABD_LR1.dbf", props, "FIRST", "DISTANCE", "ZERO", "FIELDS", "M_DIRECTON")
arcpy.LocateFeaturesAlongRoutes_lr(pts, nhd2, "REACHCODE", "1000 Meters", "Puget_NABD_LR2.dbf", props, "FIRST", "DISTANCE", "ZERO", "FIELDS", "M_DIRECTON")
arcpy.LocateFeaturesAlongRoutes_lr(pts, nhd3, "REACHCODE", "1000 Meters", "Puget_NABD_LR3.dbf", props, "FIRST", "DISTANCE", "ZERO", "FIELDS", "M_DIRECTON")

lr1 <- read_sf('Puget_NABD_LR1.dbf')
lr2 <- read_sf('Puget_NABD_LR2.dbf')
lr3 <- read_sf('Puget_NABD_LR3.dbf')
lr <- rbind(lr1, lr2, lr3)
dams$RID <- lr$RID[match(dams$NIDID, lr$NIDID)]
dams$MEAS <- lr$MEAS[match(dams$NIDID, lr$NIDID)]
dams$Distance <- lr$Distance[match(dams$NIDID, lr$NIDID)]

dams <- st_join(dams, flowlines[,c('NHDPlusID')], join=st_nearest_feature)
st_write(dams, 'Puget_NABD.shp')
```

### NHDPlusHR Pathlength and DownLevelPath
Derive Pathlength and DownLevelPath from NHDPlusHR
```{r, error=FALSE, message=FALSE, comment=FALSE , eval=FALSE}
flowlines$PathLength <- vaa$PathLength[match(flowlines$NHDPlusID, vaa$NHDPlusID)]
flowlines$HydroSeq <- vaa$HydroSeq[match(flowlines$NHDPlusID, vaa$NHDPlusID)]
flowlines$LevelPathI <- vaa$LevelPathI[match(flowlines$NHDPlusID, vaa$NHDPlusID)]
flowlines$DnHydroSeq <- vaa$DnHydroSeq[match(flowlines$NHDPlusID, vaa$NHDPlusID)]
flowlines$DnLevelPat <- vaa$DnLevelPat[match(flowlines$NHDPlusID, vaa$NHDPlusID)]
```

### NHDPlusHR Waterbodies and Catchments
```{r, error=FALSE, message=FALSE, comment=FALSE , eval=FALSE}
st_line_midpoints <- function(sf_lines = NULL) {
  g <- st_geometry(sf_lines)
  g_mids <- lapply(g, function(x) {
    coords <- as.matrix(x)

    # this is just a copypaste of View(maptools:::getMidpoints):
    get_mids <- function (coords) {
      dist <- sqrt((diff(coords[, 1])^2 + (diff(coords[, 2]))^2))
      dist_mid <- sum(dist)/2
      dist_cum <- c(0, cumsum(dist))
      end_index <- which(dist_cum > dist_mid)[1]
      start_index <- end_index - 1
      start <- coords[start_index, ]
      end <- coords[end_index, ]
      dist_remaining <- dist_mid - dist_cum[start_index]
      mid <- start + (end - start) * (dist_remaining/dist[start_index])
      return(mid)
    }

    mids <- st_point(get_mids(coords))
    })

  out <- st_sfc(g_mids, crs = st_crs(sf_lines))
  out <- st_sf(out)
}

wb1 <- read_sf(dsn='NHDPLUS_H_1708_HU4_GDB.gdb',layer='NHDWaterbody')
wb2 <- read_sf(dsn='NHDPLUS_H_1710_HU4_GDB.gdb',layer='NHDWaterbody')
wb3 <- read_sf(dsn='NHDPLUS_H_1711_HU4_GDB.gdb',layer='NHDWaterbody')
wb <- rbind(wb1, wb2, wb3)
rm(wb1, wb2, wb3)

fcode <- read_sf(dsn='NHDPLUS_H_1711_HU4_GDB.gdb',layer='NHDFcode')
wb$Desc <- fcode$Description[match(wb$FCode, fcode$FCode)]
levels(as.factor(wb$Desc))
wb <- wb %>% 
  dplyr::filter(!Desc %in% c('Estuary','Ice Mass')) %>% 
  dplyr::rename(WBArea_Permanent_Identifier=Permanent_Identifier)
wb$Desc <- as.factor(wb$Desc)
levels(wb$Desc) <- c("Lake/Pond", "Lake/Pond Intermittent", "Lake/Pond Intermittent","Lake/Pond Intermittent","Lake/Pond Perennial","Lake/Pond Perennial","Lake/Pond Perennial","Reservoir","Reservoir","Reservoir","Reservoir","Reservoir","Reservoir","Reservoir","Reservoir","Reservoir","Reservoir","Reservoir","Reservoir","Reservoir","Reservoir","Reservoir","Reservoir","Reservoir","Reservoir","Reservoir","Reservoir","Reservoir","Swamp/Marsh","Swamp/Marsh Intermittent","Swamp/Marsh Perennial")
wb$Desc <- as.character(wb$Desc)

wb_swamps <- flowlines %>% 
  st_line_midpoints()
flowline_atts <- flowlines %>% 
  dplyr::select(Permanent_Identifier,NHDPlusID,HydroSeq) %>%
  st_drop_geometry()
wb_swamps$Permanent_Identifier <- flowline_atts$Permanent_Identifier
wb_swamps$NHDPlusID <- flowline_atts$NHDPlusID
wb_swamps$HydroSeq <- flowline_atts$HydroSeq
# swamp / marshes don't have WBArea_Permanent_Identifier populated in NHDPlusHR
wb <- st_transform(wb, st_crs(flowlines))
wb_swamps <-st_join(wb_swamps, wb[,c('WBArea_Permanent_Identifier','GNIS_ID','GNIS_Name','AreaSqKm','Desc')])

# wb_swamps <- left_join(wb_swamps, st_drop_geometry(wb[,c('WBArea_Permanent_Identifier','AreaSqKm','Desc')]))

# Get Startflag to identify headwaters
wb_swamps$StartFlag <- vaa$StartFlag[match(wb_swamps$NHDPlusID, vaa$NHDPlusID)]

wb_swamps <- wb_swamps %>%
  dplyr::filter(!is.na(WBArea_Permanent_Identifier))

wb_swamps$HydroSeq[is.na(wb_swamps$HydroSeq)] <- 0
wb_swamps$StartFlag[is.na(wb_swamps$StartFlag)] <- 0

canals <- flowlines %>% 
  dplyr::filter(FType==336) %>% 
  dplyr::select(Type=FType)

cat1 <- read_sf(dsn='NHDPLUS_H_1708_HU4_GDB.gdb',layer='NHDPlusCatchment')
cat2 <- read_sf(dsn='NHDPLUS_H_1710_HU4_GDB.gdb',layer='NHDPlusCatchment')
cat3 <- read_sf(dsn='NHDPLUS_H_1711_HU4_GDB.gdb',layer='NHDPlusCatchment')
cats <- rbind(cat1, cat2, cat3)
rm(cat1, cat2, cat3)
canals <- st_transform(canals, st_crs(cats))
cats <- st_join(cats, canals)
canals <- cats %>% 
  dplyr::filter(!is.na(Type) & !duplicated(NHDPlusID))
```

### Associate NHDPlusV21 MMI with NHDPlusHR flowlines
```{r, error=FALSE, message=FALSE, comment=FALSE , eval=FALSE}
mmi <- read_csv('NRSA_PredictedBioCondition_Region_allstreams17.csv')
# get downstream points of streams
flowlines_simple <- st_cast(flowlines, "LINESTRING")
stream_points <- st_line_sample(flowlines_simple, sample = 1)
stream_points <- st_sf(stream_points)
stream_points$NHDPlusID <- flowlines$NHDPlusID[match(row.names(stream_points),row.names(flowlines))]
cats <- read_sf('Catchment.shp')
cats <- st_transform(cats, st_crs(stream_points))
NHD_catCOM <- st_join(stream_points, cats)
NHD_catCOM <- NHD_catCOM %>% 
  dplyr::select(NHDPlusID,COMID=FEATUREID)
NHD_catCOM$MMI <- mmi$prG_BMMI[match(NHD_catCOM$COMID, mmi$COMID)]
flowlines$MMI <- NHD_catCOM$MMI[match(flowlines$NHDPlusID, NHD_catCOM$NHDPlusID)]
```

### Downstream Dispersal Calculation
Gather Upstream segments within 5km of sites
to calculate downstream scores
```{r, error=FALSE, message=FALSE, comment=FALSE , eval=FALSE}
sites <- sites %>% 
  dplyr::filter(!duplicated(SITE_ID))
sites$ddi <- 0
sites$upstream_count <- 0
sites$upstream_NA <- 0
sites$upstream_small_dams <- 0
sites$upstream_large_dams <- 0
sites$upstream_canals <- 0
sites$upstream_lakes <- 0
sites$upstream_swamps <- 0
sites$upstream_crossings <- 0
sites$upstream_flowlength <- 0
sites$upstream_mean_MMI <- 0

sites_buf <- st_buffer(sites, dist=5000)

for (k in 1:nrow(sites)){
  print (paste0('working on ', as.character(st_drop_geometry(sites[k, c('SITE_ID')]))))
  
  temp_com <- as.double(st_drop_geometry(sites[k,c('COMID')]))
  temp_reach <- as.double(st_drop_geometry(sites[k,c('REACHCODE')]))
  temp_reach_meas <- as.double(st_drop_geometry(sites[k,c('REACH_meas')]))
  
  Upstream <- get_UT(flowlines, temp_com, distance = 10)
  if (Upstream==55000800000008){
    Upstream2 <- get_UT(flowlines,  55000800051691, distance = 10)
    Upstream = c(Upstream, Upstream2)
  }

  Up_streams <- flowlines %>% 
    dplyr::filter(NHDPlusID %in% Upstream)
  Up_streams <- st_intersection(Up_streams, sites_buf[k,])
  
  Up_dams <- dams %>% 
    dplyr::filter(NHDPlusID %in% Up_streams$NHDPlusID & !(RID == temp_reach & MEAS < temp_reach_meas))
  Up_dams <- Up_dams[sites_buf[k,],]
  
  Up_crossings <- road_strms %>% 
    dplyr::filter(NHDPlusID %in% Up_streams$NHDPlusID & !(NHDPlusID == temp_com & REACH_meas < temp_reach_meas))
  Up_crossings <- Up_crossings[sites_buf[k,],]
  
  Up_canals <- canals %>% 
    dplyr::filter(NHDPlusID %in% Up_streams$NHDPlusID)
  Up_canals <- st_transform(Up_canals, st_crs(sites_buf))
  Up_canals <- Up_canals[sites_buf[k,],]
  
  Up_wb_swamp <- wb_swamps %>% 
    dplyr::filter(NHDPlusID %in% Up_streams$NHDPlusID) %>%
  dplyr::group_by(WBArea_Permanent_Identifier) %>% 
    dplyr::filter(any(StartFlag!=1)) %>%
    dplyr::filter(HydroSeq == min(HydroSeq))
  
  #dist_decay
  Up_streams$dist <- Up_streams$PathLength - min(Up_streams$PathLength)

  Up_streams <- Up_streams %>% 
    mutate(dist_decay = case_when(
      dist < 1 ~ 1,
      dist >= 1 ~ (1/dist^2)))
  
  Up_streams$ddi <- 1
  if (nrow(Up_dams) >0){
    for (i in 1:nrow(Up_dams)){
      temp_weight <- as.double(st_drop_geometry(Up_dams[i, c('down_weight')]))
      up_temp <- get_UT(Up_streams, as.double(st_drop_geometry(Up_dams[i, c('NHDPlusID')])), distance = 5)
      Up_streams$ddi[Up_streams$NHDPlusID %in% up_temp] <- Up_streams$ddi[Up_streams$NHDPlusID %in% up_temp] * temp_weight 
    }
  }

  if (nrow(Up_crossings) > 0){  
    for (i in 1:nrow(Up_crossings)){
      temp_weight <- .6
      up_temp <- get_UT(Up_streams, as.double(st_drop_geometry(Up_crossings[i, c('NHDPlusID')])), distance = 5)
      print (i)
      print (up_temp)
      Up_streams$ddi[Up_streams$NHDPlusID %in% up_temp] <- Up_streams$ddi[Up_streams$NHDPlusID %in% up_temp] * temp_weight
    }
  }

  if (nrow(Up_canals) >0){
    for (i in 1:nrow(Up_canals)){
      temp_weight <- .4
      up_temp <- get_UT(Up_streams, as.double(st_drop_geometry(Up_canals[i, c('NHDPlusID')])), distance = 5)
      print (i)
      print (up_temp)
      Up_streams$ddi[Up_streams$NHDPlusID %in% up_temp] <- Up_streams$ddi[Up_streams$NHDPlusID %in% up_temp] * temp_weight
    }
  }

  if (nrow(Up_wb_swamp) >0){
    for (i in 1:nrow(Up_wb_swamp)){
      if (st_drop_geometry(Up_wb_swamp[i,c('Desc')]) %in% c('Lake/Pond Perennial','Lake/Pond Intermittent')) temp_weight <- .8
      if (st_drop_geometry(Up_wb_swamp[i,c('Desc')]) %in% c("Swamp/Marsh", "Swamp/Marsh Perennial","Swamp/Marsh Intermittent")) temp_weight <- .6
      up_temp <- get_UT(Up_streams, as.double(st_drop_geometry(Up_wb_swamp[i, c('NHDPlusID')])), distance = 5)
      print (i)
      print (up_temp)
      Up_streams$ddi[Up_streams$NHDPlusID %in% up_temp] <- Up_streams$ddi[Up_streams$NHDPlusID %in% up_temp] * temp_weight
    }
  }

  # Incorporate MMI, stream Length, and dist decay
  Up_streams$MMI_dummy <- Up_streams$MMI
  Up_streams$MMI_dummy[is.na(Up_streams$MMI_dummy)] <- 1
  Up_streams$ddi <- Up_streams$ddi * Up_streams$MMI_dummy * Up_streams$dist_decay * Up_streams$LengthKM
  
  sites[k,c('ddi')] <- sum(Up_streams$ddi,na.rm = FALSE)
  sites[k,c('upstream_count')] <- nrow(Up_streams)
  sites[k,c('upstream_NA')] <- nrow(Up_streams[is.na(Up_streams$MMI),])
  sites[k,c('upstream_large_dams')] <- nrow(Up_dams[Up_dams$down_weight==0,])
  sites[k,c('upstream_small_dams')] <- nrow(Up_dams[Up_dams$down_weight==0.5,])
  sites[k,c('upstream_canals')] <- nrow(Up_canals)
  sites[k,c('upstream_lakes')] <- nrow(Up_wb_swamp[Up_wb_swamp$Desc %in% c('Lake/Pond Perennial','Lake/Pond Intermittent'),])
  sites[k,c('upstream_swamps')] <- nrow(Up_wb_swamp[Up_wb_swamp$Desc %in% c("Swamp/Marsh","Swamp/Marsh Perennial","Swamp/Marsh Intermittent"),])
  sites[k,c('upstream_crossings')] <- nrow(Up_crossings)
  sites[k,c('upstream_flowlength')] <- as.numeric(units::set_units(sum(st_length(Up_streams)), km))
  sites[k,c('upstream_mean_MMI')] <- mean(Up_streams$MMI,na.rm = T)
}  
```

### Upstream Dispersal calculation
Gather Downstream segments within 5km of sites to calculate upstream scores
```{r, error=FALSE, message=FALSE, comment=FALSE, eval=FALSE}
sites$udi <- 0
sites$downstream_count <- 0
sites$downstream_NA <- 0
sites$downstream_small_dams <- 0
sites$downstream_large_dams <- 0
sites$downstream_canals <- 0
sites$downstream_large_lakes <- 0
sites$downstream_small_lakes <- 0
sites$downstream_swamps <- 0
sites$downstream_crossings <- 0
sites$downstream_flowlength <- 0
sites$downstream_mean_MMI <- 0

for (k in 1:nrow(sites)){
  print (paste0('working on ', as.character(st_drop_geometry(sites[k, c('SITE_ID')]))))
  temp_com <- as.double(st_drop_geometry(sites[k,c('COMID')]))
  temp_reach <- as.double(st_drop_geometry(sites[k,c('REACHCODE')]))
  temp_reach_meas <- as.double(st_drop_geometry(sites[k,c('REACH_meas')]))
  
  Downstream <- get_DM(flowlines, temp_com, distance = 10)
  
  Down_streams <- flowlines %>% 
    dplyr::filter(NHDPlusID %in% Downstream)
  Down_streams <- st_intersection(Down_streams, sites_buf[k,])
  #dist_decay
  Down_streams$dist <- abs(Down_streams$PathLength - max(Down_streams$PathLength))
  
  Down_streams <- Down_streams %>% 
    mutate(dist_decay = case_when(
      dist < 1 ~ 1,
      dist >= 1 ~ (1/dist^2)))
  
  Down_dams <- dams %>% 
    dplyr::filter(NHDPlusID %in% Down_streams$NHDPlusID & !(RID == temp_reach & MEAS > temp_reach_meas))
  Down_dams <- Down_dams[sites_buf[k,],]
  
  Down_crossings <- road_strms %>% 
    dplyr::filter(NHDPlusID %in% Down_streams$NHDPlusID & !(NHDPlusID == temp_com & REACH_meas > temp_reach_meas))
  Down_crossings <- Down_crossings[sites_buf[k,],]
  
  Down_canals <- st_transform(Down_canals, st_crs(sites_buf))
  Down_canals <- canals %>% 
    dplyr::filter(NHDPlusID %in% Down_streams$NHDPlusID)
  Down_canals <- Down_canals[sites_buf[k,],]
  
  Down_wb_swamp <- wb_swamps %>%
    dplyr::filter(NHDPlusID %in% Down_streams$NHDPlusID) %>%
  group_by(WBArea_Permanent_Identifier) %>%
    dplyr::filter(HydroSeq == max(HydroSeq))
  
  Down_streams$udi <- 1
  if (nrow(Down_dams) >0){
    for (i in 1:nrow(Down_dams)){
      temp_weight <- as.double(st_drop_geometry(Down_dams[i, c('up_weight')]))
      down_temp <- get_DM(Down_streams, as.double(st_drop_geometry(Down_dams[i, c('NHDPlusID')])), distance = 5)
      Down_streams$udi[Down_streams$NHDPlusID %in% down_temp] <- Down_streams$udi[Down_streams$NHDPlusID %in% down_temp] * temp_weight 
    }
  }
  
  if (nrow(Down_crossings) >0){  
    for (i in 1:nrow(Down_crossings)){
      temp_weight <- .4
      down_temp <- get_DM(Down_streams, as.double(st_drop_geometry(Down_crossings[i, c('NHDPlusID')])), distance = 5)
      print (i)
      print (down_temp)
      Down_streams$udi[Down_streams$NHDPlusID %in% down_temp] <- Down_streams$udi[Down_streams$NHDPlusID %in% down_temp] * temp_weight
    }
  }
  
  if (nrow(Down_canals) >0){
    for (i in 1:nrow(Down_canals)){
      temp_weight <- .9
      down_temp <- get_DM(Down_streams, as.double(st_drop_geometry(Down_canals[i, c('NHDPlusID')])), distance = 5)
      print (i)
      print (down_temp)
      Down_streams$udi[Down_streams$NHDPlusID %in% down_temp] <- Down_streams$udi[Down_streams$NHDPlusID %in% down_temp] * temp_weight
    }
  }
  
  if (nrow(Down_wb_swamp) >0){
    for (i in 1:nrow(Down_wb_swamp)){
      if (st_drop_geometry(Down_wb_swamp[i,c('Desc')]) %in% c('Lake/Pond Perennial','Lake/Pond Intermittent') & st_drop_geometry(Down_wb_swamp[i,c('AreaSqKm')]) >- 19) temp_weight <- .1
      if (st_drop_geometry(Down_wb_swamp[i,c('Desc')]) %in% c('Lake/Pond Perennial','Lake/Pond Intermittent') & st_drop_geometry(Down_wb_swamp[i,c('AreaSqKm')]) < 2) temp_weight <- .9    
      if (st_drop_geometry(Down_wb_swamp[i,c('Desc')]) %in% c("Swamp/Marsh","Swamp/Marsh Perennial","Swamp/Marsh Intermittent")) temp_weight <- .75
      down_temp <- get_DM(Down_streams, as.double(st_drop_geometry(Down_wb_swamp[i, c('NHDPlusID')])), distance = 5)
      print (i)
      print (down_temp)
      Down_streams$udi[Down_streams$NHDPlusID %in% down_temp] <- Down_streams$udi[Down_streams$NHDPlusID %in% down_temp] * temp_weight
    }
  }
  
  # Incorporate MMI, stream Length, and dist decay
  
  Down_streams$MMI_dummy <- Down_streams$MMI
  Down_streams$MMI_dummy[is.na(Down_streams$MMI_dummy)] <- 1
  Down_streams$udi <- Down_streams$udi * Down_streams$MMI_dummy * Down_streams$dist_decay * Down_streams$LengthKM
  sites[k,c('udi')] <- sum(Down_streams$udi,na.rm = FALSE)
  
  sites[k,c('downstream_count')] <- nrow(Down_streams)
  sites[k,c('downstream_NA')] <- nrow(Down_streams[is.na(Down_streams$MMI),])
  sites[k,c('downstream_large_dams')] <- nrow(Down_dams[Down_dams$up_weight==.25,])
  sites[k,c('downstream_small_dams')] <- nrow(Down_dams[Down_dams$up_weight==0.8,])
  sites[k,c('downstream_canals')] <- nrow(Down_canals)
  sites[k,c('downstream_large_lakes')] <- nrow(Down_wb_swamp[Down_wb_swamp$Desc %in% c('Lake/Pond Perennial','Lake/Pond Intermittent') & Down_wb_swamp$AreaSqKm >= 19,])
  sites[k,c('downstream_small_lakes')] <- nrow(Down_wb_swamp[Down_wb_swamp$Desc %in% c('Lake/Pond Perennial','Lake/Pond Intermittent') & Down_wb_swamp$AreaSqKm < 2,])
  sites[k,c('downstream_swamps')] <- nrow(Down_wb_swamp[Down_wb_swamp$Desc %in% c("Swamp/Marsh","Swamp/Marsh Perennial","Swamp/Marsh Intermittent"),])
  sites[k,c('downstream_crossings')] <- nrow(Down_crossings)
  sites[k,c('downstream_flowlength')] <- as.numeric(units::set_units(sum(st_length(Down_streams)), km))
  sites[k,c('downstream_mean_MMI')] <- mean(Down_streams$MMI,na.rm = T)
}
```